Probabilistic Inference of Stellar Parameters:\\ Application to Flickering Stars \altaffilmark{\titledag}

### 2015-05-07 version1.0/introduction.tex
leaving with Dave

The demand for probilistic stellar parameters not only motivated by the fact
that probability distributions are far more representative of our `beliefs'
about astrophysical parameters, but also

@@

% We use the example of flicker; the brightness fluctuations of stars on
% timescales less than 8 hours, which has been shown to correlate both with
% surface gravity and stellar density, to demonstrate our probilistic approach.

% Previous studies calibrating the relations between flicker, surface
% gravity and stellar density have assumed that the relations between these
% properties are deterministic, i.e. if you know the flicker of a star with
% infinite precision, then you can exactly predict the dependant property.
% We here provide a probabilistic recalibration of the relations between surface
% gravity, stellar density and flicker, allowing for the astrophysical
% dispersion in the relation.
% This probabilitic recalibration will produce predictive {\it distributions}
% for stellar density and surface gravity, given a measurement of flicker.

% use of HBMs, particularly for exoplanets lately

% Here we introduce an application of HBMs to fundamental stellar
% characterization specifically for flicker.

>>>>

The demand for probilistic stellar parameters not only motivated by the fact
that probability distributions are far more representative of our `beliefs'
about astrophysical parameters, but also... (ruth will continue this sentence)

@@
